Comprehensive study of the global phase diagram of the $J$-$K$-$\Gamma$ model on a triangular lattice

### 2021-01-24 paper/paper.tex
Paper 2021-01-24 14:02

In order to better understand the quantum phases identified by the ED method, we also perform classical Monte Carlo simulations. We begin with paralleling-tempering Monte Carlo~\cite{Hukushima96} on 40 replicas with temperature $T/J$ ranging from $0.001$ to $1.0$. For each replica, we sample it with a combination of heat-bath~\cite{Miyatake84} and over-relaxation method~\cite{Berg} mainly on a $24 \times 24$ triangle lattice with periodic boundary conditions. A whole Monte Carlo step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice. We perform $10^6$ Monte Carlo steps per replica, then, we copy out the spin configuration from the lowest-T replica, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the GS. The zero-temperature heat-bath sampling is simply aligning the spins according to their local fields:
\begin{align}
    \vec{S}_{i} = \frac{\vec{h}_{i}^{loc}}{|\vec{h}_{i}^{loc}|} S,
\end{align}
with
\begin{align}
    \vec{h}_{i}^{loc} = \sum_{\langle j \rangle} J \vec{S}_{j} + K {S}^{\gamma}_{j} \hat{e}^{\gamma} + \Gamma (S^{\alpha}_{j} \hat{e}^{\beta} + S^{\beta}_{j} \hat{e}^{\alpha}),
\end{align}
\added[swang]{and the over-relaxation sampling is just mirror reflection of a spin with respect to the local field:
\begin{eqnarray}
    \vec{S}_i^{new} & = &\frac{2 (\vec{S}_i^{old} \cdot \vec{h}_i^{loc}) \vec{h}_i^{loc}}{|\vec{h}_i^{loc}|^2}-\vec{S}_i^{old}.
\end{eqnarray}
}For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.

>>>>

In order to better understand the quantum phases identified by the ED method, we also perform classical Monte Carlo simulations. We begin with paralleling-tempering Monte Carlo~\cite{Hukushima96} on 40 replicas with temperature $T/J$ ranging from $0.001$ to $1.0$. For each replica, we sample it with a combination of heat-bath~\cite{Miyatake84} and over-relaxation method~\cite{Berg} mainly on a $24 \times 24$ triangle lattice with periodic boundary conditions. A whole Monte Carlo step consists of a single heat-bath sweep and subsequent 10 over-relaxation sweeps over the entire lattice. We perform $10^6$ Monte Carlo steps per replica, then, we copy out the spin configuration from the lowest-T replica, and sample it with a combination of zero-temperature heat-bath and over-relaxation method to get the GS. The zero-temperature heat-bath sampling is simply aligning the spins according to their local fields:
\begin{align}
    \vec{S}_{i} = \frac{\vec{h}_{i}^{loc}}{|\vec{h}_{i}^{loc}|} S,
\end{align}
with
\begin{align}
    \vec{h}_{i}^{loc} = \sum_{\langle j \rangle} J \vec{S}_{j} + K {S}^{\gamma}_{j} \hat{e}^{\gamma} + \Gamma (S^{\alpha}_{j} \hat{e}^{\beta} + S^{\beta}_{j} \hat{e}^{\alpha}),
\end{align}
\added[swang]{
    and the over-relaxation sampling is just mirror reflection of a spin with respect to the local field:
    \begin{eqnarray}
        \vec{S}_i^{new} & = &\frac{2 (\vec{S}_i^{old} \cdot \vec{h}_i^{loc}) \vec{h}_i^{loc}}{|\vec{h}_i^{loc}|^2}-\vec{S}_i^{old}.
    \end{eqnarray}
}
For some competing states, we start from several different initial configurations in order to obtain the correct classical GS.
